\begin{appendices}
\chapter{User stories and cards}\label{ap:userstories}

\subsection*{User userstories}
\begin{itemize*}
\item As a user i want to be able to copy and share urls, so that i can navigate to any given state of the app.
\item As a user I want to see my navigation bar on top, so that i have quick overview of my main options.
\item As a user I want to log in through Github, so that i can see my assignments and manage my course
\item As a user i want to be able to switch modes of autograder, so that i can use it in student mode for courses i attend and teacher mode for courses i teach
\item As a user I want to toggle between different courses.
\item As a user i want to have quick access to most used actions, so that it is easier to navigate.
\item As a user I want to access profile settings, so that I can change email, student number and display name.

\subsection*{Student userstories}
\item As a student i want to se current courses I attend, so that i can easily see due dates and slipdays.
\item As a student I want to view a list of available courses that I can join.
\item As a student i want to create new group, so that other students can join for group assignment.
\item As a student I want to look at my assignments so that I can see the progress
\item As a student I want to list all my assignments so that I can view how many there are.
\item As a student I want to see the members of my group so that I can track the group progress.
\item As a student I want to see the group progress and be notified when changes are made in the group so that all group members know the current status of the group assignment 

\subsection*{Admin userstories}
\item As an admin I want an initial setup page for AG so that I can easily define paths and other parameters.
\item As an admin I want to see all teachers in one place so that it becomes easier to manage.
\item As an admin I want to view a list of all courses in the system so that I can manage them all in one place.
\item As an admin I want to list all current students so that I can manage permissions (admin,teacher,student)
\item As an admin I want to see a list of all users so that I view activity of each user. (slipdays etc.)
\item As an admin I want a list of all students so that I can search for an individual student without having to use the browsers search function
\item As a admin I want to be notified of important events (define events ?) to better manage user permissions.

\subsection*{Teacher userstories}
\item As a teacher I want to view a list of courses so that I can see which courses I teach.
\item As a teacher I want to easily see results for each lab, so that i dont have to look for individual labs.
\item As a teacher I want to be able to easily create groups for assignments, so that i don't have to approve student created groups.
\item As a teacher I want see the progress of assignments so that I can track number of slipdays and progress of my students.
\item As a teacher I want to be able to access setting, so that i can change the course details ++.
\item As a teacher I want to view a list of students so that I can see a all the students attending my course.
\item As a teacher I want to be notified of any important events in real time, so that i can respond accordingly
\item As a teacher I want to be notified when students exceed their slipday-count so that I can ask what they are doing in my course
\item As a teacher I want to select an organization from github so that I can create new courses on AG.
\item As a teacher I want a list of all students so that I can search for an individual student without using the browsers search function
\item As a teacher I want to easily switch between courses, so that I can choose relevant course faster.
\item As a teacher I want to archive / delete course, so that I can see only relevant and active courses.
\item As a teacher I want to export grades and student numbers for a course, so that I can see grades separately.
\end{itemize*}
\end{appendices}

