\documentclass[12pt, a4paper]{report}
\begin{document}

\section{Introduction}
10 pages. Purpose of the thesis

\section{Background med teknologi}
20-30 pages. Summary of the subfields (technology etc)

Wireframes, User stories
Requirements (what functionality the system needs, techer mode, student mode etc..);
ReactJS..React vs AngularJS..Angular
Flux vs MVC

Storage, DB
Golang, Go
WebSocket

\section{Design and architechitecture}
20-30 pages. Explain the problem and design of our experiments.

Explain all wireframes
Flux (detailed)
Present the whole system (fig)
 Go deeper in each section, zoom in on elements (explain why these solutions)
WebSocket
Database
Server
Cli
Cli<->Server

\section{Implementation}
10-20 pages. How we implemented the shit.
Reflect on des/arch but with code

\section{Discussion}
20-30 pages.Self critical analysis of UI

\section{Conclusion}
5 pages. Summarize what you did, what worked and what didn’t.
Discuss potential future work that may fill gaps in your work, or approaches that
seem promising to overcome problems you encountered but that you weren’t able
to tackle.
This is we write togeder later ok m8? =)

\section{Appendices}
Include any material that would break the flow of the main body
of your thesis in appendices. For example, appendices often include presentation
of non-essential data; long proofs; elaborations of ideas for future work; code
listings or other “methods” information (circuit designs and suchlike), and other
documentation such as user guides.

User stories, trello

\section{Dictionary}

Remember to write a short summary before the chapter text starts. 
Make sure the chapter title reflects the content of the chapter.

React
WebSocket
Front-end
Back-end
Client-side
Server-side
Autograder
Go


\end{document}